---
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(bbccIR)

knitr::opts_chunk$set(warning = FALSE, message = FALSE, results = FALSE, eval = FALSE)

```

# bbccIR 0.0.9000

[Edgar Zamora | Twitter: `@Edgar_Zamora_`](https://twitter.com/Edgar_Zamora_)


To install the `bbccIR` package run the following code:
```{r installation}
devtools::install_github("Edgar-Zamora/bbccIR")
```

# Data Warehouse Tables
The following sections detail transformations, visualations, and/or calculations that can be made to the tables that are found within our data warehouse (e.g. transcripts, class, student, etc.). For the functions to work you have to retrieve and store the table as a R object.

# Transcript Table

### `clean_dw_transcript`

The `clean_dw_transcript` function will remove those courses that are not neccessary when looking at course level data. This function will be important when producing course success rates. 

There are two different ways to use the `clean_dw_transcript` function. The first method is by passing the data object that contains the transcript table directly into the function as so:

```{r clean_transcript1}
clean_dw_transcript(transcript_tbl)
```

The second method is using the pipe (%>%) as so:

```{r clean_transcript2}
transcript_tbl %>% 
  clean_dw_transcript()
```

### `course_success_rate`

Using the `course_success_rate` will generate an output that calculates the pass rate for every course taught at BBCC. To do so you will need to have the entire transcript table saved as an object in R. 

There are two methods to use the `course_success_rate`, both equal in their output. The first method is by passing the data object that contains the transcript table directly into the function as so:

```{r course_success1}
course_success_rate(transcript_tbl) %>%
  filter(year > "B89")
```

The second method is using the pipe (%>%) as so:

```{r course_success2}
transcript_tbl %>% 
  course_success_rate() %>% 
  filter(total_stu >= 5, 
         year == "B90")
```


# BBCC Theme
## Big Bend Community Bend (BBCC)

```{r bbcc}
ggplot(mtcars, aes(mpg, qsec, fill = as.factor(cyl))) +
  geom_point() +
  labs(title = "Miles per Gallon (MPG) v. 1/4 mile time") +
  theme_bbcc()
```

# Image Rights

All imaging included are owned by their respective colleges.

# Credits

Inspired by Bob Rudis' (hrbrthemes), Ryo Nakagawara' (tvthemes).....
